The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-16 paper.tex
update

 Followed by the forward shock is a turbulent and hot plasma.\
 As shown in the temperature or density slices of the fiducial run,\
 the full extent of the turbulent plasma is approximately agree with\
 that of the \textit{Fermi} bubbles \citep{Su2010}.
 Also, the temperature of the plasma is as high as 2 keV, comparable to that inside the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
 We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
 suggesting the outer edge of the \textit{Fermi} bubbles\
 is a tangling contact discontinuity rather than a shock.

>>>>

 Followed by the forward shock is a turbulent and hot plasma.\
 As shown in the temperature or density slices of the fiducial run,\
 the full extent of the turbulent plasma is approximately agree with\
 that of the \textit{Fermi} bubbles \citep{Su2010}.
 Also, the temperature of the plasma is as high as 2 keV, comparable to that inside the \textit{Fermi} bubbles\
 by observing X-ray absorption lines through the hot\
 gaseous halo along many different sight lines in the sky \citep{Miller_2013}.\
 We also note that the turbulence within the hot plasma is in pressure balance with the external medium,\
 suggesting the outer edge of the \textit{Fermi} bubbles\
 is a tangling contact discontinuity rather than a smooth shock.
